\centerline{\bf ÖZET}
\addcontentsline{toc}{section}{ÖZET}
\begin{center}
\textbf{Projenin Amacı}
\end{center} 
\begin{small}
Çeşitli sensör ve devre elemanlarının birbirleri ile ve mobil uygulama ile anlık haberleşmesini sağlayarak endüstri 4.0 ile beraber gelen nesnelerin interneti üzerine bir proje geliştirmektir.
\end{small}

\begin{center}
\textbf{Projenin Kapsamı}
\end{center}
\begin{small}
Projemizde göstermelik olsa'da bir devre kurulacaktır. Bu devre bir sunucuya bulunduğu ortamda'ki ısı, nem ve gaz değerlerini gönderirken aynı zamanda sürekli olarak sunucuda ki verileri okuyacak ve gelen veriye göre elektrikli sistemlerin kontrolünü sağlayacaktır. Aynı şekilde mobil uygulamada hem sunucudan gelen değerleri okuyup-yazacak hemde sunucuya veri gönderecekdir. Böylece mobil uygulama ve devre sürekli olarak haberleşmiş olacaktır.
\end{small}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%ABSTRACT%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\centerline{\bf ABSTRACT}
\addcontentsline{toc}{section}{ABSTRACT}
\begin{center}
\textbf{Project Objective}
\end{center}


\begin{small}
Developing a project on the IOT that comes with industry 4.0 by providing instant communication of various sensors and circuit elements with each other and with the mobile application.
\end{small}
%Bilecik Şeyh Edebali University Department of Computer Engineering students is studied. The aim of project is work to create a template for writing \LaTeX\ writing the final report template in the Project, to be written.

\begin{center}
\textbf{Scope of Project}
\end{center}
\begin{small}
A circuit will be established in our project, even if it is only for show. While this circuit sends the temperature, humidity and gas values of the environment to a server, it will also continuously read the data on the server and control the electrical systems according to the incoming data. Likewise, in the mobile application, it will both read and write the values from the server and send data to the server. Thus, the mobile application and the circuit will be in constant communication.
\end{small}
%Bilecik Şeyh Edebali University Computer Engineering Department Bilecik need to create a project template Latex codes assignment, involves the use of. The first part of the project consists of two parts, \LaTeX's development have been studied and why it is preferred that the use of information provided in the information. Faculty of Engineering of the university for the second part, Sheikh Edebali Bilecik Project Paper \LaTeX\ codes and are included.


%As a result, Bilecik Sheikh Edebali University Computer Engineering
%Department prepared a document that students can build project reports into \LaTeX. 